TimeVaryingDetection_mrmr

### 2024-11-16 code/R/54188_ClassicCustomComparison_mrmr.Rmd
update formatting and clean up code

**Classic mrmr model vs. modified mrmr model**

    The modified model...

@@

**Load packages**
```{r}
library(cmdstanr)
library(mrmr)
library(ggpubr)
```

## Run 54188 data through my custom model

**Load and clean data**
```{r}
# set paths for 54188 captures and surveys
captures <- read.csv("/Users/johnimperato/Desktop/Mossy-Pond/data/54188_capture.csv")  
surveys <- read.csv("/Users/johnimperato/Desktop/Mossy-Pond/data/54188_survey.csv")

@@

```{r}
# Fit the custom model using the modified function
custom_mod_54188 <- fit_model_custom(data_custom_mod_54188,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

custom_mod_54188_summary <- custom_mod_54188$m_fit$summary()
View(custom_mod_54188_summary)

write.csv(custom_mod_54188_summary, "54188_custom_mod_summary")

@@

**Plot abundance and recruitment**
```{r}

@@

**Visual Comparison**
```{r}

>>>>

**Classic mrmr model vs. custom mrmr model**

The custom model...

@@

**Load packages**

```{r}
library(cmdstanr)
library(mrmr)
library(ggpubr)
```

## Run 54188 data through custom model

**Load and clean data**

```{r}
# set paths for 54188 captures and surveys
captures <- read.csv("/Users/johnimperato/Desktop/Mossy-Pond/data/54188_capture.csv")  
surveys <- read.csv("/Users/johnimperato/Desktop/Mossy-Pond/data/54188_survey.csv")

@@

**Fit the custom model**

```{r}
# Fit the custom model using the modified function
custom_mod_54188 <- fit_model_custom(data_54188,
                                chains = 3, 
                                iter_sampling = 1000, 
                                iter_warmup = 400)

# create and view model summary
custom_mod_54188_summary <- custom_mod_54188$m_fit$summary()
View(custom_mod_54188_summary)

# save results to .csv file
write.csv(custom_mod_54188_summary, "54188_custom_mod_summary")

@@

**Plot abundance and recruitment**

@@

**Visual Comparison**
